Abstract

### 2025-05-14 output/Letter_to_editor_reviewers.Rmd
Make minor rephrasings in letter

@@

We think the motivation and psychometric utility of our approach are more related to the interpretation of the item parameters than with the latent abilities.
To our understanding, the better interpretation of the item parameters that results from our approach provides indeed a better insight into how the results are used.
A multidimensional representation of the items provides benchmarks for comparing different latent trait levels, as discussed by @reckase_difficulty_1985.
Therefore, the more accurate such a representation is, the better the latent trait interpretation will be.

Please see our answer in p. 3 of this letter for an example of how the interpretation of the item parameters may change when considering the covariance structure.
<!-- TODO: Complete -->

@@

We intended to refer to section 4.8 (*Distance and Angle in General Cartesian Coordinates*), where it is explained how to compute coordinates that "involve the inclination of the reference axes" [@harman_modern_1976, p. 60].
Please note that, as we do not have access to the 2nd edition anymore, we have used the 3rd one in our new version, and updated all the references accordingly.

@@

We think that our word choice has been unfortunate here.
What we want to imply is that there are two different spaces, the latent space, and the test space, and that, unlike the latent traits, which "naturally lie" in the latent space, the item parameters "naturally lie in the test space", even though they can be projected onto the latent space.
This is implicit in the definition of the test space itself (see p. 7 line 8 in our original submission, or p. <!-- TODO: Complete --> line <!-- TODO: Complete --> in the new version), and is independent of the basis chosen.

We argue that the test space and the latent space are two distinct spaces, even when the basis of the latent space (and, consequently, that of the test space) is orthonormal.
It is our understanding that,  due to a lack of need for this distinction, this is overlooked in Reckase's [-@reckase_difficulty_1985] and Reckase & McKinley's [-@reckase_discriminating_1991] original formulations.
We have added this latter clarification in our new version (p. <!-- TODO: Complete --> lines <!-- TODO: Complete -->):

>>>>

We acknowledge and apologize for the lack of clarity in this sentence.
Please refer to our 10th response to Reviewer 3 in p. <!-- TODO: Complete --> of this letter.

@@

We think the motivation and psychometric utility of our approach are more related to the interpretation of the item parameters than with the latent abilities, which we believe exceeds the scope of this manuscript and could be the focus of another paper.
Please note that we only use the transformation in the latent space to an orthonormal basis as a reasoning artifact to obtain the proper expression of the item parameters in the general case, and that we do it in an abstract sense, before even considering whether the original basis is a representation of the covariance matrix.

However, to our understanding, the more precise interpretation of the item parameters that results from our approach provides indeed a better insight into how the results are used.
A multidimensional representation of the items provides benchmarks for comparing different latent trait levels, as discussed by @reckase_difficulty_1985.
Therefore, the more accurate such a representation is, the better the latent trait interpretation will be.

Please see our answer in p. <!-- TODO: Complete (3?) --> of this letter for an example of how the interpretation of the item parameters may change when considering the covariance structure.
<!-- TODO: Complete -->

@@

We intended to refer to section 4.8 (*Distance and Angle in General Cartesian Coordinates*), where he explains how to compute coordinates that "involve the inclination of the reference axes" [@harman_modern_1976, p. 60].
Please note that, as we do not have access to the 2nd edition anymore, we have used the 3rd one in our new version, and updated all the references accordingly.

@@

We think that our word choice has been unfortunate here.
What we want to imply is that there are two different spaces, the latent space, and the test space, and that, unlike the latent traits, which "naturally lie" in the latent space, the item parameters "naturally lie in the test space", even though they can be projected onto the latent space.
This is implicit in the definition of the test space itself (see p. 7 line 8 in our original submission, or p. <!-- TODO: Complete --> line <!-- TODO: Complete --> in the new version), and is independent of the basis chosen, which does not necessarily need to be a geometric representation of the covariance structure, as we argue in our introduction.

We also argue that the test space and the latent space are two distinct spaces, even when the basis of the latent space (and, consequently, that of the test space) is orthonormal.
It is our understanding that,  due to a lack of need for this distinction, this is overlooked in Reckase's [-@reckase_difficulty_1985] and Reckase & McKinley's [-@reckase_discriminating_1991] original formulations.
We have added this latter clarification in our new version (p. <!-- TODO: Complete --> lines <!-- TODO: Complete -->):
